---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Dyn4cast

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange)](#)
    [![R build status](https://github.com/JobNmadu/Dyn4cast/workflows/R-CMD-check/badge.svg)](https://github.com/JobNmadu/Dyn4cast/actions)
    [![Codecov test coverage](https://codecov.io/gh/Jeniffen/projectr/branch/master/graph/badge.svg)](https://codecov.io/gh/JobNmadu/Dyn4cast?branch=master)
<!-- badges: end -->

 The __Dyn4cast__ package is designed to be a lightweight package, with the 
    aim of simplifying the estimation, prediction and forecast of time-varying daraset, especially where the data is cntining and is routine. The package takes away the efforts of putting together a library of more than than packages which were used to develop it. 

## Installation

Althouth it would be possible to install the released version of Dyn4cast from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("Dyn4cast")
```
presently, only the development version is available.

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JobNmadu/Dyn4cast")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Dyn4cast)
## basic example code
niz2 <- readxl::read_excel("F:/Dyn4cast/R/data/Data.xlsx")
niz2$Date <- as.Date(niz2$Date, format = '%m/%d/%Y')

Dss <- seq(niz2$Date[1], by = "day", length.out = length(niz2$Case))
lastdayfo21 <- Dss[length(Dss)]
KK_28 <- niz2[niz2$Date <= lastdayfo21 - 28, ]
Days_28 <- DynamicForecast(Data = KK_28, BREAKS = c(70, 131, 173, 228, 274) , Date = "2021-02-10")

knitr::kable(as.data.frame(Days_28$Forecast), row.names = FALSE, "html")
knitr::kable(as.data.frame(Days_28$RMSE), "html")
Days_28$Plot

```


